---
title: "myLM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myLM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(myLM)
```

Installation:

```{r}
#devtools::install_github("wjhlang/myLM")
library(myLM)
```

## Basic usage of function `myLM`:
To explore the usage of `myLM`, we'll use the dataset `iris`. This dataset contains `r nrow(data("iris"))` observations and `r ncol(data("iris"))` columns.
```{r}
data("iris")
x = iris$Petal.Width
y = iris$Petal.Length
myLM(y~x)
# Equivalently

myLM(Petal.Length~Petal.Width, data = iris)

# This gives the exact same result as the original lm function
lm(Petal.Length~Petal.Width, data = iris)
```

# Usage of different parameters
Usage of weights

```{r}
# Get random numbers from the uniform distribution as the weights
rand = runif(nrow(iris))
myLM(Petal.Length~Petal.Width,data = iris, weights = rand)

# Compare with the lm function
lm(Petal.Length~Petal.Width,data = iris, weights = rand)
```

Usage of subset

```{r}
myLM(Petal.Length~Petal.Width,data = iris, subset = "Petal.Width<2")

# Compare with the lm function
lm(Petal.Length~Petal.Width,data = iris, subset = Petal.Width<2)
```
Usage of method

```{r}
head(myLM(Petal.Length~Petal.Width,data = iris, method = "model.frame"))

# Compare with the lm function
all.equal(as.matrix(myLM(Petal.Length~Petal.Width,data = iris, method = "model.frame")), as.matrix(lm(Petal.Length~Petal.Width,data = iris, method = "model.frame")))
```

Usage of model: Slight optimization that outputs the interaction term as well.

```{r}
head(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, model = T)$model) # Same as myLM(Petal.Length~Petal.Width,data = iris)

# Compare with the lm function
head(lm(Petal.Length~Petal.Width*Sepal.Width,data = iris, model = T)$model)
```
Use of x, y

```{r}
head(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$x)
head(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$y)

# Compare with the lm function
all.equal(as.matrix(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$x),as.matrix(lm(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$x))
all.equal(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$y,lm(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$y)
```
Summary (benefites of the 'lm' class)

```{r}
summary(myLM(Petal.Length~Petal.Width*Sepal.Width + log(Petal.Width),data = iris))
# Compare with the lm function
summary(lm(Petal.Length~Petal.Width*Sepal.Width + log(Petal.Width),data = iris))
```

Diagnostic Plots (benefites of the 'lm' class)

```{r}
par(mfrow=c(2,2))
par(mar=c(2,2,2,2))
plot(myLM(Petal.Length~Petal.Width*Sepal.Width + I(Sepal.Length)^2,data = iris))
# Compare with the lm function
par(mfrow=c(2,2))
par(mar=c(2,2,2,2))
plot(lm(Petal.Length~Petal.Width*Sepal.Width + I(Sepal.Length)^2,data = iris))
```

Compare efficiency

```{r}
bnch = bench::mark(myLM(Petal.Length~Petal.Width*Sepal.Width + I(Sepal.Length)^2,data = iris)$coefficients, lm(Petal.Length~Petal.Width*Sepal.Width + I(Sepal.Length)^2,data = iris)$coefficients)
bnch
```

The lack efficiency might be due to that I'm trying to implement everything in the original function,which slows down the process a bit.

