---
title: "myLM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myLM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(myLM)
```

Installation:

```{r}
#devtools::install_github("wjhlang/myLM")
library(myLM)
```

## Basic usage of function `myLM`:
To explore the usage of `myLM`, we'll use the dataset `iris`. This dataset contains `r nrow(data("iris"))` observations and `r ncol(data("iris"))` columns. We'll also be using simulated data in the examples later on.
```{r}
data("iris")
x = iris$Petal.Width
y = iris$Petal.Length
myLM(y~x)
# Equivalently

myLM(Petal.Length~Petal.Width, data = iris)

# This gives the exact same result as the original lm function
lm(Petal.Length~Petal.Width, data = iris)
```

Simulated dataset

```{r, eval=FALSE}
y = x%*%rnorm(5,1,10) + rnorm(10000,0,0.5)
x = matrix(rnorm(50000), nrow=10000) 
simdata = as.data.frame(cbind(y,x))
colnames(simdata) = c("y", "x1", "x2", "x3", "x4", "x5")
```
```{r}
data("simdata")
```

# Usage of different parameters
Usage of weights

```{r}
# Get random numbers from the uniform distribution as the weights
rand = runif(nrow(iris))
myLM(Petal.Length~Petal.Width,data = iris, weights = rand)

# Compare with the lm function
lm(Petal.Length~Petal.Width,data = iris, weights = rand)

# On simulated dataset
# Get random numbers from the uniform distribution as the weights
rand = runif(nrow(simdata))
myLM(y~x1+x2+x3+x4+x5, data = simdata, weights = rand)

# Compare with the lm function
lm(y~., data = simdata,weights = rand)
```

Usage of subset

```{r}
myLM(Petal.Length~Petal.Width,data = iris, subset = "Petal.Width<2")

# Compare with the lm function
lm(Petal.Length~Petal.Width,data = iris, subset = Petal.Width<2)

# On simulated dataset
rand = runif(nrow(simdata))
myLM(y~x1+x2+x3+x4+x5, data = simdata, subset = "x5<3")

# Compare with the lm function
lm(y~., data = simdata,subset = x5<3)
```
Usage of method

```{r}
head(myLM(Petal.Length~Petal.Width,data = iris, method = "model.frame"))

# Compare with the lm function
all.equal(as.matrix(myLM(Petal.Length~Petal.Width,data = iris, method = "model.frame")), as.matrix(lm(Petal.Length~Petal.Width,data = iris, method = "model.frame")))

# On simulated dataset
head(myLM(y~x1+x2+x3+x4+x5, data = simdata, method = "model.frame"))

# Compare with the lm function
comp1 = as.matrix(myLM(y~x1+x2+x3+x4+x5, data = simdata, method = "model.frame"))
colnames(comp1) = NULL
comp2 = as.matrix(lm(y~., data = simdata, method = "model.frame"))
colnames(comp2) = NULL
all.equal(comp1, comp2)
```

Usage of model: Slight optimization that outputs the interaction term as well.

```{r}
head(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, model = T)$model) # Same as myLM(Petal.Length~Petal.Width,data = iris)

# Compare with the lm function
head(lm(Petal.Length~Petal.Width*Sepal.Width,data = iris, model = T)$model)

# On simulated dataset
head(myLM(y~x1+x2+x3+x4+x5,data = simdata)$model)

# Compare with the lm function
all.equal(as.matrix(myLM(y~x1+x2+x3+x4+x5,data = simdata)$model), as.matrix(lm(y~.,data=simdata)$model))
```
Use of x, y

```{r}
head(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$x)
head(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$y)

# Compare with the lm function
all.equal(as.matrix(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$x),as.matrix(lm(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$x))
all.equal(myLM(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$y,lm(Petal.Length~Petal.Width*Sepal.Width,data = iris, x = T, y = T)$y)

# On simulated dataset
all.equal(as.matrix(myLM(y~x1+x2+x3+x4+x5,data = simdata, x = T, y = T)$x),as.matrix(lm(y~.,data = simdata, x = T, y = T)$x))
all.equal(myLM(y~x1+x2+x3+x4+x5,data = simdata, x = T, y = T)$y,lm(y~.,data = simdata, x = T, y = T)$y)
```

Summary (benefites of the 'lm' class)

```{r}
summary(myLM(Petal.Length~Petal.Width*Sepal.Width + log(Petal.Width),data = iris))
# Compare with the lm function
summary(lm(Petal.Length~Petal.Width*Sepal.Width + log(Petal.Width),data = iris))

# On simulated dataset
summary(myLM(y~x1+x2+x3+x4+x5,data = simdata))
# Compare with the lm function
summary(lm(y~.,data = simdata))
```

Diagnostic Plots (benefites of the 'lm' class)

```{r}
par(mfrow=c(2,2))
par(mar=c(2,2,2,2))
plot(myLM(Petal.Length~Petal.Width*Sepal.Width + I(Sepal.Length)^2,data = iris))
# Compare with the lm function
par(mfrow=c(2,2))
par(mar=c(2,2,2,2))
plot(lm(Petal.Length~Petal.Width*Sepal.Width + I(Sepal.Length)^2,data = iris))

# On simulated dataset
par(mfrow=c(2,2))
par(mar=c(2,2,2,2))
plot(myLM(y~x1+x2+x3+x4+x5,data = simdata))
# Compare with the lm function
par(mfrow=c(2,2))
par(mar=c(2,2,2,2))
plot(lm(y~.,data = simdata))
```

Compare efficiency

```{r}
formula = Petal.Length~Petal.Width*Sepal.Width + I(Sepal.Length)^2
bnch1 = bench::mark(myLM(formula,data = iris)$coefficients, lm(formula,data = iris)$coefficients)
bnch1[,1] = c("myLM()", "lm()")
bnch1

# On simulated dataset
bnch2 = bench::mark(myLM(y~x1+x2+x3+x4+x5,data = simdata)$coefficients, lm(y~.,data = simdata)$coefficients)
bnch2[,1] = c("myLM()", "lm()")
bnch2
```

The lack of efficiency might be due to that I'm trying to implement everything that's being outputted in the original function, which slows down the process a bit.

